Papers

### 2024-05-10 quarto/index.qmd
update

* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
	*"Imagine reading a book without figures: Multimodal-CoT surpasses humans on ScienceQA."*
	In *arXiv*, 2023<br>
	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>

>>>>

* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
	In *Transactions on Machine Learning Research*, 2023<br>
	<a href="https://twitter.com/astonzhangAZ/status/1621545166049005568" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
	<a href="img/mm-cot-idea.png" target="_blank">[Idea Inspiration by Homeschooling]</a>
